How to Schedule Periodic Messages in a Network Without Congestion

### 2017-06-02 article/article.tex
quelques petites corrections

%opening
\title{How to Schedule Periodic Messages in a Network Without Congestion}
\author{DB,CC,MG,OM,YS}

@@

      \begin{figure}[ht]
      % \begin{center}

@@

\end{tikzpicture}
     % \end{center}
       \caption{A routage graph with $(0,0,0)$ as a $(2,1)$-periodic assignment}
      \end{figure}

@@

      The following experimental results compare the three presented algorithms.
      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time. We will compare the performance of the algorithms in two different regimes: the routes are either short with regards to $\tau$ and $P$ or unrestricted.
      We choose the parameter realistic with regard to our C-RAN context. The number of routes 
      is at most $n = 20$, $\tau$ is equal to $2500$ and the period is at most $3n\tau$ (otherwise the greedy algorithm always returns a solution). The code in C is available online on the webpages of the authors ~\cite{webpage}.
%             
%             The graphs 
%       To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
% 
%       \todo{Mettre les données concrètes plus proprement et éventuellement ne pas les mettre si on envoie pas à un truc de télécom}

@@

      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithms which justifies its use. 
      However for small period, less than $30000$ the computation time is really important and without improvements it would not be possible to tackle 
      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods less than $22000$, we see that there are very few instances with a solution for PAZL. It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting time.

@@

	  We just found solution to solve a restricted version of PALL, in which no waiting times are allowed, 
	  and the problem has no solution when the period is too short. We propose to allow some message to wait in the target vertices (BBU), with the aim of giving an higher degree of freedom for the scheduling. Thus, the process time of a message $PT$ might be superior to $T_{max}$. The goal is to find some solutions with waiting time such that any message will be buffered too much, i.e. $MT({\cal M}) \leq T_{max}$.

@@

	Another particular case is the following one:	
	 \begin{theorem}
      There is always an optimal solution when all the weight on the arcs between $c_s$ and the sources are the same.
      \end{theorem}
      \begin{proof}

@@

    \begin{algorithm}[H]
    \caption{Longest Shortest Greedy (LSG)}
    \begin{algorithmic}
    \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, $ T_{max}$, packet size $\tau$
    \ENSURE $(P-\tau)-$periodic assignment of ${\cal R_{\cal C}}$
    \STATE $clock \leftarrow 0$
    \FORALL{route i in $r_{s_i}$ sorted from the longest to the shortest }
    \STATE  $m_{s_i} \leftarrow clock - t(c_s,r_{s_i}) \mod P$
    \STATE $clock \leftarrow clock + \tau$
    \ENDFOR

@@

    By using a binary heap to manage the eligible routes, this algorithm runs in $\mathcal{O}(n\log{}n)$.

@@

     However, this heuristic does not take the period into account . Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might need a too large period.

     \subsection{Sending order}

	We tried to look at the behavior of the that policy with different kind of sending order for the messages.

@@

    \begin{algorithm}[H]
    \caption{ Minimized Scheduling Periodic (MSP)}
    \begin{algorithmic}
    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
    \ENSURE $(P-\tau)-$periodic assignment of ${\cal R_{\cal C}}$, if it exists

@@

     The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic assignment, even with a small period, and T$_{max}$.

@@

     In our case of 8 routes, the number of different sending orders is $8! \simeq 40 000$. By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending oredres.

     We now want to compare the performances of the different algorithms.Since GP showed some excellent results on large periods (see Figure 5), it is more interesting to focus on the behavior of the algorithms on short periods. The following experience is realized on graph with 8 routes (links between $0$ and $20000$), and with a period of 21000. Since we just conclude that drawing 1000 sending order is a good number, with 8 routes. We now generate 1000 randoms sending orders for the first way.

       \begin{center}
      \includegraphics[scale=0.4]{retour_21000.pdf}
      \end{center}
      \caption{Success rate of the different algorithms for a $P = 21000$}
     \end{figure}

@@

   We plan to generalize our study of the PALL problem to more topology,
   such as trees and cycles which are the most common ones in real networks. 
   We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the contraint on the maximal process time into an constraint on the average process time, which seems much more tractable. 
   Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces,
   which could certainly change the complexity of the problem. 
   Finally, the routes may not be fixed but chosen to optimize the latency, which would make the problem even more difficult ( maybe $\Pi_2$-complete instead of $\NP$-complete).

>>>>

%opening
\title{How to Schedule Periodic Messages in a Network Without Congestion}
%\author{Dominique Barth - UVSQ ,Christian Cadéré - UVSQ,Maël Guiraud - UVSQ,Olivier Marcé - Nokia Bell Labs France,Yann Strozecki - UVSQ}

\author{
   Dominique {\bf Barth}, {\em UVSQ}
   \and
   Christian  {\bf Cad\'er\'e}, {\em UVSQ}
      \and
   Ma\"el  {\bf Guiraud}, {\em UVSQ}
      \and
   Olivier  {\bf Marcr\'e}, {\em Nokia Bell Labs France}
      \and
   Yann  {\bf Strozecki}, {\em UVSQ}
}

@@

      \begin{figure}[ht]
      \begin{center}
          \scalebox{0.8}{

@@

}
     \end{center}
       \caption{A routage graph with $(0,0,0)$ as a $(2,1)$-periodic assignment}
      \end{figure}

@@

      The following experimental results compare the three presented algorithms.
      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time. We will compare the performance of the algorithms in two different regimes: the routes are either short with regards to $\tau$ and $P$ or unrestricted.
      We choose the parameter realistic with regard to our C-RAN context. The number of routes 
      is at most $n = 20$, $\tau$ is equal to $2500$ and the period is at most $3n\tau$ (otherwise the greedy algorithm always returns a solution). The code in C is available online on the webpages of the authors ~\cite{webpage}.
%             
%             The graphs 
%       To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
% 
%       \todo{Mettre les donn√©es concr√®tes plus proprement et √©ventuellement ne pas les mettre si on envoie pas √† un truc de t√©l√©com}

@@

      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithms which justifies its use. 
      However for small period, less than $30000$ the computation time is really important and without improvements it would not be possible to tackle 
      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods less than $22000$, we see that there are very few instances with a solution for PAZL. It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting times.

@@

    In this section, we allow the messages to wait in the target vertices (BBU), to give an higher degree of freedom to the scheduling. Thus, the process time of a message $PT$ might be superior to $T_{max}$. The goal is to find a solution with waiting time such that any message will be not be buffered too much, i.e. $MT({\cal M}) \leq T_{max}$.

@@

	Another particular case is the following one:	
	 \begin{theorem}
      There is always an optimal solution when all the weights on the arcs between $c_s$ and the sources are the same.
      \end{theorem}
      \begin{proof}

@@

    \begin{algorithm}[H]
    \caption{Longest Shortest Greedy (LSG)}
    \begin{algorithmic}
    \REQUIRE routage graph $(G,{\cal R})$, period $P$, $ T_{max}$, packet size $\tau$
    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$
    \STATE $clock \leftarrow 0$
    \FORALL{route i in $r_{s_i}$ sorted from the longest to the shortest }
    \STATE  $m_{s_i} \leftarrow clock - t(c_s,r_{s_i}) \mod P$
    \STATE $clock \leftarrow clock + \tau$
    \ENDFOR

@@

    By using a binary heap to manage the eligible routes, this algorithm runs in $O(n\log(n))$.

@@

     However, this heuristic does not take the period into account. Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might need a too large period.

     \subsection{Choice of the Sending Order}

	We tried to look at the behavior of the that policy with different kinds of sending order for the messages.

@@

    \begin{algorithm}[H]
    \caption{ Minimized Scheduling Periodic (MSP)}
    \begin{algorithmic}
    \REQUIRE A routage graph $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, if it exists

@@

     The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic assignment, even with a small period, and $T_{max}$.

@@

     In our case of 8 routes, the number of different sending orders is $8! \simeq 40 000$. By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending ordres.

     We now want to compare the performances of the different algorithms.Since GP showed some excellent results on large periods (see  Fig~\ref{fig:success21000}), it is more interesting to focus on the behavior of the algorithms on short periods. The following experience is realized on graph with $8$ routes (links between $0$ and $20000$), and with a period of $21000$. Since we just conclude that drawing $1000$ sending order is a good number, with 8 routes. We now generate $1000$ randoms sending orders for the first way.

    \begin{figure} 
       \begin{center}
      \includegraphics[scale=0.4]{retour_21000.pdf}
      \end{center}
      \caption{Success rate of the different algorithms for a $P = 21000$}
     \label{fig:success21000}
     \end{figure}

@@

   We plan to generalize our study of the PALL problem to more topologies,
   such as trees and cycles which are commonly found in real networks. 
   We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the constraint on the maximal process time into an constraint on the average process time, which seems much more tractable. 
   Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces,
   which would certainly change the complexity of the problem. 
   Finally, the routes may not be fixed but chosen to optimize the latency, which would make the problem even more difficult (maybe $\Pi_2$-complete instead of $\NP$-complete).
